\documentclass[10pt]{article}

\usepackage{csquotes}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{relsize}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage[a4paper,bottom=1in,top=1in,left=1in,right=1in]{geometry}
\usepackage[hidelinks]{hyperref}

\newcommand{\Rplus}{\protect\raisebox{0.35ex}{\smaller{\smaller{\textbf{+}}}}}
\newcommand{\Rsharp}{\protect\raisebox{0.35ex}{\smaller{\smaller{\textbf{\#}}}}}
\newcommand{\Cpp}{\mbox{C\Rplus\Rplus}}
\newcommand{\Csharp}{\mbox{C\Rsharp}}
\newcommand{\firstpar}{\vspace{4pt}\noindent}

\titleformat{\subsection}[display]{\large\scshape}{\thesubsection}{}{}[\vspace{-4pt}]
\titleformat{\section}[display]{\Large\bfseries}{\thesection}{}{\vspace{-8pt}}[\hrule\vspace{-4pt}]

\begin{document}

% Contact Information
\begin{table}
    \begin{center}
        {\Huge \scshape Andrew Bilsborough} \\

        \vspace{4pt}
        {\Large \scshape Software Engineer} \\

        \vspace{2pt}
        \small \faHome\ Cedarburg, WI, United States ~
        \href{tel:+12626652710}{\faPhone\ \Rplus 1 (262) 665-2710} \\

        \vspace{2pt}
        \href{mailto:bilsborough.andrewj@gmail.com}{\faEnvelope\ \texttt{bilsborough.andrewj@gmail.com}} ~
        \href{https://www.linkedin.com/in/andrew-bilsborough-9123a123a/}
        {\faLinkedin\ \texttt{andrew-bilsborough-9123a123a}}  ~
        \href{https://github.com/Lindelt}{\faGithub\ \texttt{Lindelt}}
        \vspace{-20pt}
    \end{center}
\end{table}

\section*{Education}
\subsection*{Lakeland University}
\textbf{B.S. Computer Science}, 2017---2022 \\
Economics Minor, 3.48 GPA

\section*{Employment History}
\subsection*{Badger Technology Group}
\begin{tabular}{@{}ll@{}}
    \textbf{Software Engineering Intern} & May 2023 -- August 2023 \\
    \textbf{Software Engineer}           & August 2023 -- Present
\end{tabular}

\firstpar
Badger Technology Group, Inc. is a US-based Systems Engineering and Hardware/Software development
company and was established with a focus on providing unique systems integration capabilities and
solutions drawing on expert software, hardware and systems engineers from leading technology and
aerospace companies and the US military
(\href{https://badgertg.com/about}{\texttt{https://badgertg.com/about}}).

\begin{itemize}[noitemsep, leftmargin=*]
    \item Created AS9100-compliant software archival solution.
    \item Implemented customer requirements for prototype Primary Flight and 3-ATI Displays.
    \item Documented pre-existing internal processes.
    \item Designed and documented an internal development and testing asset (server rack).
\end{itemize}

\section*{Volunteering}
\subsection*{Revitalize Milwaukee}
\begin{tabular}{@{}ll@{}}
    \textbf{Technical Consultant} & August 2020 -- Present
\end{tabular}

\firstpar
Revitalize Milwaukee is a 501(c)3 nonprofit organization whose goal is to reduce social, economic,
and environmental disparities by providing free home repairs throughout Milwaukee and Waukesha counties
(\href{https://www.freehomerepairs.org/our-mission}{\texttt{https://www.freehomerepairs.org/our-mission}}).

\begin{itemize}[noitemsep, leftmargin=*]
    \item Partnered with management to optimize and maintain planning software.
    \item Applied database design principles to optimize software setup and operations.
    \item Created and maintained dashboards to enable management to assign and track tasks and project completion.
    \item Monitored data quality to eliminate duplicate data.
    \item Troubleshot and resolved software and data issues.
\end{itemize}

\section*{Technical Skills}
\begin{tabularx}{\textwidth}{@{}>{\bfseries}l>{\raggedright\arraybackslash}X@{}}
    Programming Languages   &
    \Cpp, \Csharp, Haskell, Java, PowerShell, Python, Rust, SQL \\
    Frameworks \& Libraries &
    OpenGL 2.0 SC, ZMQ                                          \\
    Tools                   &
    CMake, Git, GitHub, Inkscape, \mbox{Power Automate}, \mbox{Visual Studio}, \mbox{Visual Studio Code}
\end{tabularx}

\section*{Projects}
\paragraph{2013 First Robotics Competition}
\vline\quad \Cpp, Eclipse \hfill 2012---2013

\noindent
\textit{Cedarburg High School}

\firstpar
Lead programmer for the CHS robotics team. Implemented the majority of the design
requirements, tested the produced robot, and managed robot code performance during
the competition.

\paragraph{Note Taking Mobile Application}
\vline\quad Java, Android Studio \hfill 2022

\noindent
\textit{Lakeland University}

\firstpar
Developed as part of a mobile applications development class. Focus was on creating a minimal
viable product with a consistent visual style and clean code base.

\paragraph{\href{https://github.com/Lindelt/java-either}{\faGithub\ Lindelt/java-either}}
\vline\quad Java \hfill 2022

\noindent
\textit{Personal Project}

\firstpar
An error-handling monadic type implemented in Java SE8, comparable to Haskell's \texttt{Either} or
Rust's \texttt{Result}.

\paragraph{Primary Flight Display Prototpye}
\vline\quad \Cpp, CMake, OpenGL SC 2.0, Visual Studio \hfill 2023

\noindent
\textit{Badger Technology Group}

\firstpar
A primary flight display prototype for the Calidus B-250 utilizing ZMQ to receive flight data
and OpenGL to draw the display elements.

\paragraph{3-ATI Display Prototpye}
\vline\quad \Cpp, CMake, OpenGL SC 2.0, Visual Studio \hfill 2023

\noindent
\textit{Badger Technology Group}

\firstpar
A fork of the primary flight display prototype modified for use on a $400\!\times\!400$ 3-ATI
standby display.

\section*{References}
\begin{multicols}{2}
    \raggedcolumns

    \subsection*{Lynnea Katz-Petted}
    \textbf{Chief Executive Officer} \\
    \textit{Revitalize Milwaukee} \\
    \href{mailto:lynnea@rtmilwaukee.org}{\faEnvelope\ \texttt{lynnea@rtmilwaukee.org}}

    \subsection*{Daniel Wade}
    \textbf{President \& Founder} \\
    \textit{Badger Technology Group} \\
    \href{mailto:d.wade@badgertg.com}{\faEnvelope\ \texttt{d.wade@badgertg.com}}
\end{multicols}

\end{document}